---
title: "case3_markdown"
author: "Tianye Song"
date: "11/7/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## sensus data keys

There are various kinds of data in the sensus data collected. What are they?

```{r data interpretation}
## this will print out the list of folder names in data directory, which gives some initial impression of the types of data. 
global<-dir('~/Documents/sys6018_cs3_data/round_2/') 
print(global)
```

The quantity of data is massive. It would then be wise to remove some of the uninteresting data..
At first glance, "BatteryDatum" does not interest me. "CellTowerDatum" does not interest me either.

```{r taking out unwanted folder names}
## remove batteryDatum and celltowerDatum from list of attributes interested in. 
global <- global[-c(3,4)]
print(global)
```

There are 20 entries left. Start investigating on the most strange ones.
Let's start with AccelerometerDatum.

```{r include=FALSE}
library(SensusR) # import SensusR library to read in and parse data
data.path = system.file("extdata", "example_data", package="SensusR")
data = sensus.read.json(data.path)
head(data$AccelerometerDatum)
```
 
Looks like accelerometer data contains (x,y,z) tuples that describe the location of the device (perhaps acceleration of the device) in the 3D space. 

My investigation is mainly focused on HR. Keep this data for now since this records the spatial aspect of the device, further the wrist of the device user.

Keep on investigating.
```{r investigating AltitudeDatum}
head(data$AltitudeDatum)
```

As the name suggests, AltitudeDatum records how much 'up' the user is. This could be interesting considering the user's altitude will change when he/she steps up stairs, and the action of stepping up stairs could have effects on user's Heart Rate.

So next, what is the LightDatum?

```{r investigating LightDatum}
head(data$LightDatum)
```

LightDatum measures the brightness. Not interested in this for now.. delete.
```{r taking out lightDatum}
global <- global[-3]
print(global)
```

next, look at location datum. This should be useful..

```{r investigating location datum}
head(data$LocationDatum)
```

the locationDatum records (lat, long) tuples with corresponding accuracy rating for each measurement. Defnitely worth keeping. 

next look at MicrosoftBandContactDatum, MicrosoftBandDistanceDatum, MicrosoftBandGsrDatum
```{r investigating MicrosoftBandContactDatum}
head(data$MicrosoftBandContactDatum)  

```
looks like all the data with MicrosoftBand[a-z]* are missing in the example data set. Keep them there for now.

what about ParticipationRewardDatum?
```{r investigating ParticipationRewardDatum}
head(data$ParticipationRewardDatum)  
```
emm... can't make much sense.

and PointOfInterestProximityDatum?
```{r investigating PointOfInterestProximityDatum}
head(data$PointOfInterestProximityDatum)  
```
Null in example data.

and ProtocolReportDatum
```{r investigating ProtocolReportDatum}
head(data$ProtocolReportDatum)  
```
This data looks like the usage conditions by the user. Does not seem interesting. 
```{r take out ProtocolReportDatum}
global <- global[-12]
print(global)
```

Now ScreenDatum
```{r investigating ScreenDatum}
head(data$ScreenDatum)  
```
this is the on/off situation of the screen of the band. not interesting. 

```{r take out ScreenDatum}
global <- global[-12]
print(global)
```

Now ScriptDatum
```{r investigating ScriptDatum}
head(data$ScriptDatum)  
```

can't make sense.

Now ScriptRunDatum
```{r investigating ScriptRunDatum}
head(data$ScriptRunDatum)  
```

can't make sense.

Now SmsDatum
```{r investigating SmsDatum}
head(data$SmsDatum)  
```
Null. 

SoundDatum
```{r investigating SoundDatum}
head(data$SoundDatum)  
```
the sound of the surrounding environment. Potentially interesting. Decided to keep. 

TelephonyDatum
```{r investigating TelephonyDatum}
head(data$TelephonyDatum)  
```
the call duration of the user. not interested. take out.
```{r take out TelephonyDatum}
global <- global[-16]
print(global)
```

WlanDatum
```{r investigating WlanDatum}
head(data$WlanDatum)  
```
describing network connection situation. not interested. take out
```{r take out WlanDatum}
global <- global[-16]
print(global)
```
